EvoSuite at the SBST 2015 Tool Competition

### 2015-02-21 papers/sbst15/paper_sbst15.tex
Paper editing

\begin{abstract}
  \EVOSUITE is a mature research prototype that automatically
  generates unit tests for Java code.  This paper summarizes the
  results and experiences in participating at the third unit testing
  competition held at SBST 2015. An unfortunate issue of conflicting
  dependency versions in two out of the nine projects used in the
  benchmark reduced \EVOSUITE's overall score to $190.6$, and thus the
  second rank.
\end{abstract}

@@

This paper describes the results of applying the \EVOSUITE test
generation tool~\cite{FrA11c} to the benchmark used in the tool
competition at the International Workshop on Search-Based Software
Testing (SBST) 2015.  Details on the competition and the benchmark can
be found in~\cite{sbst2015}. In this competition, \EVOSUITE ranked
second with a score of $190.6$.

@@

As the generated unit tests are meant for human
consumption~\cite{fraser2013does}, \EVOSUITE applies various
post-processing steps to improve readability (e.g., minimising) and
adds test assertions that capture the current behavior of the tested
classes. To select the most effective assertions, \EVOSUITE uses
mutation analysis~\cite{10.1109/TSE.2011.93}.  \EVOSUITE can also be
used to automatically find faults in the CUTs~\cite{emse13_oracle},
e.g., undeclared thrown exceptions and broken code contracts.  For
more details on the tool and its abilities we refer to~\cite{FrA11c},
and for more implementation details we refer to~\cite{FrA13a}.

@@

We configured \EVOSUITE to use a dynamic timeout of maximum 10 minutes
for the search, with an earlier stop if the fitness value did not
increase for two minutes. The fitness function to drive the genetic
algorithm was based on a combination of line coverage, branch
coverage, and weak mutation testing. We enabled the post-processing
step of test minimization, but to reduce the time spent we included
all assertions rather than filtering them with mutation
analysis~\cite{10.1109/TSE.2011.93}. In practice, this may not result
in the most readable or maintainable test cases, but neither of these
two attributes is measured by the SBST contest metric.

@@

Out of 63 CUTs, \EVOSUITE did not manage to obtain any coverage for 18
classes, i.e., 28\% of all classes.  For 14 of them (the 7 in the
twitter4j and the 7 in the hibernate projects), this is due to a
mismatch in libraries on the classpath.  In particular, \EVOSUITE does
bytecode instrumentation using the ASM library.  However, the projects
of the CUTs had their own (older) version of ASM.  This leads to
errors like: ``java.lang.IncompatibleClassChangeError: class
org.objectweb.asm.tree.ClassNode has interface
org.objectweb.asm.ClassVisitor as super class''.  Note: \EVOSUITE can
handle its own dependencies as CUTs, i.e., by using customized
classloaders, but only during the search phase.  In the generated
JUnit files, those have dependencies to ASM, as we do bytecode
instrumentation even there (e.g., to support environment testing based
on mock objects~\cite{arcuri2014automated}).  So, \EVOSUITE does
generate tests for those 14 classes, but then all those tests fails
due to that thrown exception.  An easy solution would be to ship
\EVOSUITE with its own ASM version using a different package name
(e.g., by using the JarJar
tool\footnote{https://code.google.com/p/jarjar/}).
%
If we had handled this issue properly before the competition, this
would have changed the result: Excluding classes from the twitter4j
and hibernate, the overall score of \EVOSUITE would be 191.584,
whereas GRT would have a score of 164.464. Consequently, this issue
clearly is the main factor affecting \EVOSUITE's overall result.

For the other four classes with 0\% coverage, \EVOSUITE failed to
generate any tests. For \<CharMatcher>, the issue is an issue in how
\EVOSUITE handled timeouts, which resulted in \EVOSUITE's master
process killing the client process before tests were written to
disk. For \<CycleHandler> and \<WikipediaInfo>, \EVOSUITE ran into an
issue when trying to resolve the generic type parameters of some
dependency classes. This issue could be avoided by omitting generic
type parameters, as the Java compiler would only issue warnings about
such missing parameters. However, as \EVOSUITE is aiming to produce
readable tests, we feel it is important to properly handle Java
Generics. Finally, for \<Response> the constructor requires a
parameter of type \<java.net.HttpURLConnection>, which is an abstract
class without concrete subclasses. As \EVOSUITE does not produce stubs
automatically, it therefore failed to instantiate \<Response> objects.

There are also a further 4 cases of low coverage (e.g., less than
30\%).  For example, if look at line coverage, then we have \<Page>
with 1.49\%, \<AbstractInstance> with 13.28\%,
\<CategoryDescendantsIterator> with 8.24\% and \<PageQueryIterable>
with 18.57\%.

TODO: Will look into these four.

>>>>

\begin{abstract}
  \EVOSUITE is a mature research prototype that automatically
  generates unit tests for Java code.  This paper summarizes the
  results and experiences of \EVOSUITE's participation at the third
  unit testing competition at SBST 2015. An unfortunate issue of
  conflicting dependency versions in two out of the nine benchmark
  projects reduced \EVOSUITE's overall score to $190.6$, leading to
  the overall second rank.
\end{abstract}

@@

This paper describes the results of applying the \EVOSUITE test
generation tool~\cite{FrA11c} to the benchmark used in the tool
competition at the International Workshop on Search-Based Software
Testing (SBST) 2015.  Details about the competition and the benchmark
can be found in~\cite{sbst2015}. In this competition, \EVOSUITE ranked
second with a score of $190.6$.

@@

As the generated unit tests are meant for human
consumption~\cite{fraser2013does}, \EVOSUITE applies various
post-processing steps to improve readability (e.g., minimising) and
adds test assertions that capture the current behavior of the tested
classes. To select the most effective assertions, \EVOSUITE uses
mutation analysis~\cite{10.1109/TSE.2011.93}.  \EVOSUITE can also be
used to automatically find faults such as undeclared thrown exceptions
and broken code contracts~\cite{emse13_oracle}.  For more details on
the tool and its abilities we refer to~\cite{FrA11c}, and for more
implementation details we refer to~\cite{FrA13a}.

@@

We configured \EVOSUITE to use a dynamic timeout of maximum 10 minutes
per class for the search, with an earlier stop if the fitness value
did not increase for two minutes. The fitness function to drive the
genetic algorithm was based on a combination of line coverage, branch
coverage, and weak mutation testing~\cite{emse14_mutation}. We enabled
the post-processing step of test minimization, but to reduce the time
spent we included all assertions rather than filtering them with
mutation analysis~\cite{10.1109/TSE.2011.93}. In practice, this may
not result in the most readable or maintainable test cases, but
neither of these two attributes is measured by the SBST contest
metric.

@@

Out of 63 classes under test (CUTs), \EVOSUITE did not manage to
obtain any coverage for 18, i.e., 28\% of all classes.  For 14 of them
(seven in the twitter4j project and seven in the hibernate project),
this is due to a mismatch in libraries on the classpath.  In
particular, \EVOSUITE does bytecode instrumentation using the ASM
library (currently using version 5.0.3).  However, the projects of the
CUTs had their own (older) version of ASM; for example Twitter4J has
an indirect dependency to ASM 3.2.

Because the API of ASM has changed over different versions, this leads
to errors like: ``java.lang.IncompatibleClassChangeError: class
org.objectweb.asm.tree.ClassNode has interface
org.objectweb.asm.ClassVisitor as super class''.  Note: \EVOSUITE can
be applied to its own library dependencies through its use of
customized classloaders. However, bytecode instrumentation is also
performed in the generated JUnit files (e.g., to support environment
testing based on mock objects~\cite{arcuri2014automated}), which leads
to a runtime dependency to ASM. Consequently, \EVOSUITE generates
tests for those 14 classes, but then all these tests fail due to the
above mentioned exception.  An easy solution would be to ship
\EVOSUITE with its own ASM version using a different package name
(e.g., by using the JarJar
tool\footnote{https://code.google.com/p/jarjar/}).
%
If we had handled this issue properly before the competition, this
would have changed the outcome: Excluding classes from the twitter4j
and hibernate, the overall score of \EVOSUITE would be 191.584,
whereas the first ranked tool (GRT) would have a score of
164.464. Consequently, this issue clearly is the main factor affecting
\EVOSUITE's overall result.

For the other four classes with 0\% coverage, \EVOSUITE failed to
generate any tests for other reasons. For \<CharMatcher>, the issue is
an issue in how \EVOSUITE handled timeouts, which resulted in
\EVOSUITE's master process killing the client process before tests
were written to disk. For \<CycleHandler> and \<WikipediaInfo>,
\EVOSUITE ran into an issue when trying to resolve the generic type
parameters of some dependency classes; this also affects \<Page> with
1.49\% coverage. This issue could be avoided by omitting generic type
parameters, as the Java compiler would only issue warnings about such
missing parameters. However, as \EVOSUITE is aiming to produce
readable tests, we feel it is important to properly handle Java
Generics. Finally, for \<Response> the constructor requires a
parameter of type \<java.net.HttpURLConnection>, which is an abstract
class without concrete subclasses. As \EVOSUITE does not produce stubs
automatically, it therefore failed to instantiate \<Response> objects.

%There are also a further 4 cases of low coverage (e.g., less than
%30\%).  For example, if look at line coverage, then we have \<Page>
%with 1.49\%, \<AbstractInstance> with 13.28\%,
%\<CategoryDescendantsIterator> with 8.24\% and \<PageQueryIterable>
%with 18.57\%.

%TODO: Will look into these four.
